---
title: "king county housing"
author: "AH-6"
date: "5/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary Table of King County housing sale

> In order to look into the King County housing data, we sorted the following table based on **zipcode** to let users compare the King county housing sale condition based on **different areas**. The price, the size of the living space, the year it is built, and the house's condition are summarized by **averaging** the data so that the data shown in the table are more **representative**. 

```{r include=FALSE}
library(knitr)
source("scripts/Aggregate Table script.R")
```

```{r echo=FALSE}
kable(summary_table(kc_housing),
      row.names = NA, 
      col.names = c("Zipcode", "Average Price", "Bedrooms", "Bathrooms", "Average living space", "Year built", "Condition"))
```

- The zipcode that has the highest housing price is `r most_expensive_zip`, which is $ `r most_expensive_price`.
- The zipcode that has the oldest houses is `r oldest_zipcode`, which was in average built back in the `r oldest_year`.

## The relationship between the housing price and the size of the living space
